---
title: "NSFG Codebook for variable `r params$varname`"
params: 
  varname: CWPALLBC02
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
    css: webdoc.css

---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
alldata <- readRDS("Data/completeNSFGmetadata.rds") %>% filter(varname == params$varname)

```


All Waves
=====================================
Column {data-width=650}
-----------------------------------------------------------------------

### Female, 2017-2019

```{r include= F}
year1 <- "201719"
type1 <- "Female"
extract <- filter(alldata, year == year1 & type == type1)
variable <- ifelse(dim(extract)[1] == 0, "Variable does not exist in this survey/wave", extract$varname)
description <- ifelse(dim(extract)[1] == 0, "", extract$question)
universe <- ifelse(dim(extract)[1] == 0, "", extract$universe)
notes    <- ifelse(dim(extract)[1] == 0 | is.na(extract$notes), "", extract$notes)
type     <- ifelse(dim(extract)[1] == 0, "", extract$vartype)
```

**Variable:** `r variable`    
**Description/Question:** `r description`    
**Type:** `r type`   
```{r echo = F}
if (dim(extract)[1] != 0) {
DT::datatable(extract$table[[1]], options = list(pageLength = 50, lengthChange = FALSE,
  bPaginate = FALSE, dom = 't', columnDefs = list(list(className = 'dt-left', targets = "_all"))
), rownames = F) %>% DT::formatStyle(names(extract$table[[1]]),lineHeight='70%') 
}

```
**Universe:** `r universe`    
**Notes:** `r notes`   

### Female, 2015-2017

```{r include= F}
year1 <- "201517"
type1 <- "Female"
extract <- alldata %>% filter(year==year1 & type == type1) 
variable <- ifelse(dim(extract)[1] == 0, "Variable does not exist in this survey/wave", extract$varname)
description <- ifelse(dim(extract)[1] == 0, "", extract$question)
universe <- ifelse(dim(extract)[1] == 0, "", extract$universe)
notes <- ifelse(dim(extract)[1] == 0 | is.na(extract$notes), "", extract$notes)
type     <- ifelse(dim(extract)[1] == 0, "", extract$vartype)
```

**Variable:** `r variable`  
**Description/Question** `r description`  
**Type:** `r type` 

```{r echo = F}
if (dim(extract)[1] != 0) {
DT::datatable(extract$table[[1]], options = list(pageLength = 50, lengthChange = FALSE,
  bPaginate = FALSE, dom = 't', columnDefs = list(list(className = 'dt-left', targets = "_all"))
), rownames = F) %>% DT::formatStyle(names(extract$table[[1]]),lineHeight='70%') 
}
```
**Universe:** `r universe`    
**Notes:** `r notes`  

### Female, 2013-2015
```{r include= F}
year1 <- "201315"
type1 <- "Female"
extract <- alldata %>% filter(year==year1 & type == type1) 
variable <- ifelse(dim(extract)[1] == 0, "Variable does not exist in this survey/wave", extract$varname)
description <- ifelse(dim(extract)[1] == 0, "", extract$question)
universe <- ifelse(dim(extract)[1] == 0, "", extract$universe)
notes <- ifelse(dim(extract)[1] == 0 | is.na(extract$notes), "", extract$notes)
type     <- ifelse(dim(extract)[1] == 0, "", extract$vartype)
```

**Variable:** `r variable`  
**Description/Question** `r description`  
**Type:** `r type` 

```{r echo = F}
if (dim(extract)[1] != 0) {


DT::datatable(extract$table[[1]], options = list(pageLength = 50, lengthChange = FALSE,
  bPaginate = FALSE, dom = 't', columnDefs = list(list(className = 'dt-left', targets = "_all"))
), rownames = F) %>% DT::formatStyle(names(extract$table[[1]]),lineHeight='70%') 
}
```
**Universe:** `r universe`    
**Notes:** `r notes`  

### Female, 2011-2013
```{r include= F}
year1 <- "201113"
type1 <- "Female"
extract <- alldata %>% filter(year==year1 & type == type1) 
variable <- ifelse(dim(extract)[1] == 0, "Variable does not exist in this survey/wave", extract$varname)
description <- ifelse(dim(extract)[1] == 0, "", extract$question)
universe <- ifelse(dim(extract)[1] == 0, "", extract$universe)
notes <- ifelse(dim(extract)[1] == 0 | is.na(extract$notes), "", extract$notes)
type     <- ifelse(dim(extract)[1] == 0, "", extract$vartype)
```

**Variable:** `r variable`  
**Description/Question** `r description`  
**Type:** `r type` 

```{r echo = F}
if (dim(extract)[1] != 0) {

DT::datatable(extract$table[[1]], options = list(pageLength = 50, lengthChange = FALSE,
  bPaginate = FALSE, dom = 't', columnDefs = list(list(className = 'dt-left', targets = "_all"))
), rownames = F) %>% DT::formatStyle(names(extract$table[[1]]),lineHeight='70%') 
}
```
**Universe:** `r universe`    
**Notes:** `r notes`  

### Female, 2006-2010
```{r include= F}
year1 <- "200610"
type1 <- "Female"
extract <- alldata %>% filter(year==year1 & type == type1) 
variable <- ifelse(dim(extract)[1] == 0, "Variable does not exist in this survey/wave", extract$varname)
description <- ifelse(dim(extract)[1] == 0, "", extract$question)
universe <- ifelse(dim(extract)[1] == 0, "", extract$universe)
notes <- ifelse(dim(extract)[1] == 0 | is.na(extract$notes), "", extract$notes)
type     <- ifelse(dim(extract)[1] == 0, "", extract$vartype)
```

**Variable:** `r variable`  
**Description/Question** `r description`  
**Type:** `r type` 

```{r echo = F}
if (dim(extract)[1] != 0) {


DT::datatable(extract$table[[1]], options = list(pageLength = 50, lengthChange = FALSE,
  bPaginate = FALSE, dom = 't', columnDefs = list(list(className = 'dt-left', targets = "_all"))
), rownames = F) %>% DT::formatStyle(names(extract$table[[1]]),lineHeight='70%') 
}
```
**Universe:** `r universe`    
**Notes:** `r notes`  

### Female, 2002
```{r include= F}
year1 <- "2002"
type1 <- "Female"
extract <- alldata %>% filter(year==year1 & type == type1) 
variable <- ifelse(dim(extract)[1] == 0, "Variable does not exist in this survey/wave", extract$varname)
description <- ifelse(dim(extract)[1] == 0, "", extract$question)
universe <- ifelse(dim(extract)[1] == 0, "", extract$universe)
notes <- ifelse(dim(extract)[1] == 0 | is.na(extract$notes), "", extract$notes)
type     <- ifelse(dim(extract)[1] == 0, "", extract$vartype)
```

**Variable:** `r variable`  
**Description/Question** `r description`  
**Type:** `r type` 

```{r echo = F}
if (dim(extract)[1] != 0) {


DT::datatable(extract$table[[1]], options = list(pageLength = 50, lengthChange = FALSE,
  bPaginate = FALSE, dom = 't', columnDefs = list(list(className = 'dt-left', targets = "_all"))
), rownames = F) %>% DT::formatStyle(names(extract$table[[1]]),lineHeight='70%') 
}
```
**Universe:** `r universe`    
**Notes:** `r notes`  

Column {data-width=650}
-----------------------------------------------------------------------

### Male, 2017-2019

```{r include= F}
year1 <- "201719"
type1 <- "Male"
extract <- alldata %>% filter(year==year1 & type == type1) 
variable <- ifelse(dim(extract)[1] == 0, "Variable does not exist in this survey/wave", extract$varname)
description <- ifelse(dim(extract)[1] == 0, "", extract$question)
universe <- ifelse(dim(extract)[1] == 0, "", extract$universe)
notes <- ifelse(dim(extract)[1] == 0 | is.na(extract$notes), "", extract$notes)
type     <- ifelse(dim(extract)[1] == 0, "", extract$vartype)
```

**Variable:** `r variable`  
**Description/Question** `r description`  
**Type:** `r type`  
```{r echo = F}
if (dim(extract)[1] != 0) {


DT::datatable(extract$table[[1]], options = list(pageLength = 50, lengthChange = FALSE,
  bPaginate = FALSE, dom = 't', columnDefs = list(list(className = 'dt-left', targets = "_all"))
), rownames = F) %>% DT::formatStyle(names(extract$table[[1]]),lineHeight='70%') 
}
```
**Universe:** `r universe`    
**Notes:** `r notes`  

### Male, 2015-2017

```{r include= F}
year1 <- "201517"
type1 <- "Male"
extract <- alldata %>% filter(year==year1& type == type1) 
variable <- ifelse(dim(extract)[1] == 0, "Variable does not exist in this survey/wave", extract$varname)
description <- ifelse(dim(extract)[1] == 0, "", extract$question)
universe <- ifelse(dim(extract)[1] == 0, "", extract$universe)
notes <- ifelse(dim(extract)[1] == 0 | is.na(extract$notes), "", extract$notes)
type     <- ifelse(dim(extract)[1] == 0, "", extract$vartype)
```

**Variable:** `r variable`  
**Description/Question** `r description`  
**Type:** `r type` 

```{r echo = F}
if (dim(extract)[1] != 0) {


DT::datatable(extract$table[[1]], options = list(pageLength = 50, lengthChange = FALSE,
  bPaginate = FALSE, dom = 't', columnDefs = list(list(className = 'dt-left', targets = "_all"))
), rownames = F) %>% DT::formatStyle(names(extract$table[[1]]),lineHeight='70%') 
}
```
**Universe:** `r universe`    
**Notes:** `r notes`  

### Male, 2013-2015
```{r include= F}
year1 <- "201315"
type1 <- "Male"
extract <- alldata %>% filter(year==year1& type == type1) 
variable <- ifelse(dim(extract)[1] == 0, "Variable does not exist in this survey/wave", extract$varname)
description <- ifelse(dim(extract)[1] == 0, "", extract$question)
universe <- ifelse(dim(extract)[1] == 0, "", extract$universe)
notes <- ifelse(dim(extract)[1] == 0 | is.na(extract$notes), "", extract$notes)
type     <- ifelse(dim(extract)[1] == 0, "", extract$vartype)
```

**Variable:** `r variable`  
**Description/Question** `r description`  
**Type:** `r type` 

```{r echo = F}
if (dim(extract)[1] != 0) {


DT::datatable(extract$table[[1]], options = list(pageLength = 50, lengthChange = FALSE,
  bPaginate = FALSE, dom = 't', columnDefs = list(list(className = 'dt-left', targets = "_all"))
), rownames = F) %>% DT::formatStyle(names(extract$table[[1]]),lineHeight='70%') 
}
```
**Universe:** `r universe`    
**Notes:** `r notes`  

### Male, 2011-2013
```{r include= F}
year1 <- "201113"
type1 <- "Male"
extract <- alldata %>% filter(year==year1& type == type1) 
variable <- ifelse(dim(extract)[1] == 0, "Variable does not exist in this survey/wave", extract$varname)
description <- ifelse(dim(extract)[1] == 0, "", extract$question)
universe <- ifelse(dim(extract)[1] == 0, "", extract$universe)
notes <- ifelse(dim(extract)[1] == 0 | is.na(extract$notes), "", extract$notes)
type     <- ifelse(dim(extract)[1] == 0, "", extract$vartype)
```

**Variable:** `r variable`  
**Description/Question** `r description`  
**Type:** `r type` 

```{r echo = F}
if (dim(extract)[1] != 0) {


DT::datatable(extract$table[[1]], options = list(pageLength = 50, lengthChange = FALSE,
  bPaginate = FALSE, dom = 't', columnDefs = list(list(className = 'dt-left', targets = "_all"))
), rownames = F) %>% DT::formatStyle(names(extract$table[[1]]),lineHeight='70%') 
}
```
**Universe:** `r universe`    
**Notes:** `r notes`  

### Male, 2006-2010
```{r include= F}
year1 <- "200610"
type1 <- "Male"
extract <- alldata %>% filter(year==year1& type == type1) 
variable <- ifelse(dim(extract)[1] == 0, "Variable does not exist in this survey/wave", extract$varname)
description <- ifelse(dim(extract)[1] == 0, "", extract$question)
universe <- ifelse(dim(extract)[1] == 0, "", extract$universe)
notes <- ifelse(dim(extract)[1] == 0 | is.na(extract$notes), "", extract$notes)
type     <- ifelse(dim(extract)[1] == 0, "", extract$vartype)
```

**Variable:** `r variable`  
**Description/Question** `r description`  
**Type:** `r type` 

```{r echo = F}
if (dim(extract)[1] != 0) {


DT::datatable(extract$table[[1]], options = list(pageLength = 50, lengthChange = FALSE,
  bPaginate = FALSE, dom = 't', columnDefs = list(list(className = 'dt-left', targets = "_all"))
), rownames = F) %>% DT::formatStyle(names(extract$table[[1]]),lineHeight='70%') 
}
```
**Universe:** `r universe`    
**Notes:** `r notes`  

### Male, 2002
```{r include= F}
year1 <- "2002"
type1 <- "Male"
extract <- alldata %>% filter(year==year1& type == type1) 
variable <- ifelse(dim(extract)[1] == 0, "Variable does not exist in this survey/wave", extract$varname)
description <- ifelse(dim(extract)[1] == 0, "", extract$question)
universe <- ifelse(dim(extract)[1] == 0, "", extract$universe)
notes <- ifelse(dim(extract)[1] == 0 | is.na(extract$notes), "", extract$notes)
type     <- ifelse(dim(extract)[1] == 0, "", extract$vartype)
```

**Variable:** `r variable`  
**Description/Question** `r description`  
**Type:** `r type` 

```{r echo = F}
if (dim(extract)[1] != 0) {


DT::datatable(extract$table[[1]], options = list(pageLength = 50, lengthChange = FALSE,
  bPaginate = FALSE, dom = 't', columnDefs = list(list(className = 'dt-left', targets = "_all"))
), rownames = F) %>% DT::formatStyle(names(extract$table[[1]]),lineHeight='70%') 
}
```
**Universe:** `r universe`    
**Notes:** `r notes`  

2017-2019 only
=====================================


Column {data-width=650}
-----------------------------------------------------------------------

### Female, 2017-2019

```{r include= F}
year1 <- "201719"
type1 <- "Female"
extract <- filter(alldata, year == year1 & type == type1)
variable <- ifelse(dim(extract)[1] == 0, "Variable does not exist in this survey/wave", extract$varname)
description <- ifelse(dim(extract)[1] == 0, "", extract$question)
universe <- ifelse(dim(extract)[1] == 0, "", extract$universe)
notes    <- ifelse(dim(extract)[1] == 0 | is.na(extract$notes), "", extract$notes)
type     <- ifelse(dim(extract)[1] == 0, "", extract$vartype)
```

**Variable:** `r variable`    
**Description/Question:** `r description`    
**Type:** `r type` 
```{r echo = F}
if (dim(extract)[1] != 0) {
DT::datatable(extract$table[[1]], options = list(pageLength = 50, lengthChange = FALSE,
  bPaginate = FALSE, dom = 't', columnDefs = list(list(className = 'dt-left', targets = "_all"))
), rownames = F) %>% DT::formatStyle(names(extract$table[[1]]),lineHeight='70%') 
}
#  generate these en masse (plus make landing page)
# pregnancy will have its own page - can hold off on making this until i get the rest working.
# Other small fixes - increase size of header
# add type. 

```
  
**Universe:** `r universe`    
**Notes:** `r notes` 

Column {data-width=650}
-----------------------------------------------------------------------

### Male, 2017-2019

```{r include= F}
year1 <- "201719"
type1 <- "Male"
extract <- alldata %>% filter(year==year1 & type == type1) 
variable <- ifelse(dim(extract)[1] == 0, "Variable does not exist in this survey/wave", extract$varname)
description <- ifelse(dim(extract)[1] == 0, "", extract$question)
universe <- ifelse(dim(extract)[1] == 0, "", extract$universe)
notes <- ifelse(dim(extract)[1] == 0 | is.na(extract$notes), "", extract$notes)
type     <- ifelse(dim(extract)[1] == 0, "", extract$vartype)
```

**Variable:** `r variable`  
**Description/Question** `r description`  
**Type:** `r type` 
```{r echo = F}
if (dim(extract)[1] != 0) {


DT::datatable(extract$table[[1]], options = list(pageLength = 50, lengthChange = FALSE,
  bPaginate = FALSE, dom = 't', columnDefs = list(list(className = 'dt-left', targets = "_all"))
), rownames = F) %>% DT::formatStyle(names(extract$table[[1]]),lineHeight='70%') 
}
```
**Universe:** `r universe`    
**Notes:** `r notes` 

2015-2017 only
=====================================
Column {data-width=650}
-----------------------------------------------------------------------

### Female, 2015-2017

```{r include= F}
year1 <- "201517"
type1 <- "Female"
extract <- alldata %>% filter(year==year1 & type == type1) 
variable <- ifelse(dim(extract)[1] == 0, "Variable does not exist in this survey/wave", extract$varname)
description <- ifelse(dim(extract)[1] == 0, "", extract$question)
universe <- ifelse(dim(extract)[1] == 0, "", extract$universe)
notes <- ifelse(dim(extract)[1] == 0 | is.na(extract$notes), "", extract$notes)
type     <- ifelse(dim(extract)[1] == 0, "", extract$vartype)
```

**Variable:** `r variable`  
**Description/Question** `r description`  
**Type:** `r type` 

```{r echo = F}
if (dim(extract)[1] != 0) {
DT::datatable(extract$table[[1]], options = list(pageLength = 50, lengthChange = FALSE,
  bPaginate = FALSE, dom = 't', columnDefs = list(list(className = 'dt-left', targets = "_all"))
), rownames = F) %>% DT::formatStyle(names(extract$table[[1]]),lineHeight='70%') 
}
```
  
**Universe:** `r universe`    
**Notes:** `r notes`  

Column {data-width=650}
-----------------------------------------------------------------------
### Male, 2015-2017

```{r include= F}
year1 <- "201517"
type1 <- "Male"
extract <- alldata %>% filter(year==year1& type == type1) 
variable <- ifelse(dim(extract)[1] == 0, "Variable does not exist in this survey/wave", extract$varname)
description <- ifelse(dim(extract)[1] == 0, "", extract$question)
universe <- ifelse(dim(extract)[1] == 0, "", extract$universe)
notes <- ifelse(dim(extract)[1] == 0 | is.na(extract$notes), "", extract$notes)
type     <- ifelse(dim(extract)[1] == 0, "", extract$vartype)
```

**Variable:** `r variable`  
**Description/Question** `r description`  
**Type:** `r type` 

```{r echo = F}
if (dim(extract)[1] != 0) {


DT::datatable(extract$table[[1]], options = list(pageLength = 50, lengthChange = FALSE,
  bPaginate = FALSE, dom = 't', columnDefs = list(list(className = 'dt-left', targets = "_all"))
), rownames = F) %>% DT::formatStyle(names(extract$table[[1]]),lineHeight='70%') 
}
```
  
**Universe:** `r universe`    
**Notes:** `r notes`  

2013-2015 only
=====================================
Column {data-width=650}
-----------------------------------------------------------------------

### Female, 2013-2015
```{r include= F}
year1 <- "201315"
type1 <- "Female"
extract <- alldata %>% filter(year==year1 & type == type1) 
variable <- ifelse(dim(extract)[1] == 0, "Variable does not exist in this survey/wave", extract$varname)
description <- ifelse(dim(extract)[1] == 0, "", extract$question)
universe <- ifelse(dim(extract)[1] == 0, "", extract$universe)
notes <- ifelse(dim(extract)[1] == 0 | is.na(extract$notes), "", extract$notes)
type     <- ifelse(dim(extract)[1] == 0, "", extract$vartype)
```

**Variable:** `r variable`  
**Description/Question** `r description`  
**Type:** `r type` 

```{r echo = F}
if (dim(extract)[1] != 0) {


DT::datatable(extract$table[[1]], options = list(pageLength = 50, lengthChange = FALSE,
  bPaginate = FALSE, dom = 't', columnDefs = list(list(className = 'dt-left', targets = "_all"))
), rownames = F) %>% DT::formatStyle(names(extract$table[[1]]),lineHeight='70%') 
}
```
  
**Universe:** `r universe`    
**Notes:** `r notes`  

Column {data-width=650}
-----------------------------------------------------------------------
### Male, 2013-2015
```{r include= F}
year1 <- "201315"
type1 <- "Male"
extract <- alldata %>% filter(year==year1& type == type1) 
variable <- ifelse(dim(extract)[1] == 0, "Variable does not exist in this survey/wave", extract$varname)
description <- ifelse(dim(extract)[1] == 0, "", extract$question)
universe <- ifelse(dim(extract)[1] == 0, "", extract$universe)
notes <- ifelse(dim(extract)[1] == 0 | is.na(extract$notes), "", extract$notes)
type     <- ifelse(dim(extract)[1] == 0, "", extract$vartype)
```

**Variable:** `r variable`  
**Description/Question** `r description`  
**Type:** `r type` 

```{r echo = F}
if (dim(extract)[1] != 0) {


DT::datatable(extract$table[[1]], options = list(pageLength = 50, lengthChange = FALSE,
  bPaginate = FALSE, dom = 't', columnDefs = list(list(className = 'dt-left', targets = "_all"))
), rownames = F) %>% DT::formatStyle(names(extract$table[[1]]),lineHeight='70%') 
}
```
  
**Universe:** `r universe`    
**Notes:** `r notes`  

2011-2013 only
=====================================

Column {data-width=650}
-----------------------------------------------------------------------
### Female, 2011-2013
```{r include= F}
year1 <- "201113"
type1 <- "Female"
extract <- alldata %>% filter(year==year1 & type == type1) 
variable <- ifelse(dim(extract)[1] == 0, "Variable does not exist in this survey/wave", extract$varname)
description <- ifelse(dim(extract)[1] == 0, "", extract$question)
universe <- ifelse(dim(extract)[1] == 0, "", extract$universe)
notes <- ifelse(dim(extract)[1] == 0 | is.na(extract$notes), "", extract$notes)
type     <- ifelse(dim(extract)[1] == 0, "", extract$vartype)
```

**Variable:** `r variable`  
**Description/Question** `r description`  
**Type:** `r type` 

```{r echo = F}
if (dim(extract)[1] != 0) {

DT::datatable(extract$table[[1]], options = list(pageLength = 50, lengthChange = FALSE,
  bPaginate = FALSE, dom = 't', columnDefs = list(list(className = 'dt-left', targets = "_all"))
), rownames = F) %>% DT::formatStyle(names(extract$table[[1]]),lineHeight='70%') 
}
```
  
**Universe:** `r universe`    
**Notes:** `r notes`  

Column {data-width=650}
-----------------------------------------------------------------------
### Male, 2011-2013
```{r include= F}
year1 <- "201113"
type1 <- "Male"
extract <- alldata %>% filter(year==year1& type == type1) 
variable <- ifelse(dim(extract)[1] == 0, "Variable does not exist in this survey/wave", extract$varname)
description <- ifelse(dim(extract)[1] == 0, "", extract$question)
universe <- ifelse(dim(extract)[1] == 0, "", extract$universe)
notes <- ifelse(dim(extract)[1] == 0 | is.na(extract$notes), "", extract$notes)
type     <- ifelse(dim(extract)[1] == 0, "", extract$vartype)
```

**Variable:** `r variable`  
**Description/Question** `r description`  
**Type:** `r type` 

```{r echo = F}
if (dim(extract)[1] != 0) {


DT::datatable(extract$table[[1]], options = list(pageLength = 50, lengthChange = FALSE,
  bPaginate = FALSE, dom = 't', columnDefs = list(list(className = 'dt-left', targets = "_all"))
), rownames = F) %>% DT::formatStyle(names(extract$table[[1]]),lineHeight='70%') 
}
```
  
**Universe:** `r universe`    
**Notes:** `r notes`  

2006-2010 only
=====================================

Column {data-width=650}
-----------------------------------------------------------------------
### Female, 2006-2010
```{r include= F}
year1 <- "200610"
type1 <- "Female"
extract <- alldata %>% filter(year==year1 & type == type1) 
variable <- ifelse(dim(extract)[1] == 0, "Variable does not exist in this survey/wave", extract$varname)
description <- ifelse(dim(extract)[1] == 0, "", extract$question)
universe <- ifelse(dim(extract)[1] == 0, "", extract$universe)
notes <- ifelse(dim(extract)[1] == 0 | is.na(extract$notes), "", extract$notes)
type     <- ifelse(dim(extract)[1] == 0, "", extract$vartype)
```

**Variable:** `r variable`  
**Description/Question** `r description`  
**Type:** `r type` 

```{r echo = F}
if (dim(extract)[1] != 0) {


DT::datatable(extract$table[[1]], options = list(pageLength = 50, lengthChange = FALSE,
  bPaginate = FALSE, dom = 't', columnDefs = list(list(className = 'dt-left', targets = "_all"))
), rownames = F) %>% DT::formatStyle(names(extract$table[[1]]),lineHeight='70%') 
}
```
  
**Universe:** `r universe`    
**Notes:** `r notes` 

Column {data-width=650}
-----------------------------------------------------------------------
### Male, 2006-2010
```{r include= F}
year1 <- "200610"
type1 <- "Male"
extract <- alldata %>% filter(year==year1& type == type1) 
variable <- ifelse(dim(extract)[1] == 0, "Variable does not exist in this survey/wave", extract$varname)
description <- ifelse(dim(extract)[1] == 0, "", extract$question)
universe <- ifelse(dim(extract)[1] == 0, "", extract$universe)
notes <- ifelse(dim(extract)[1] == 0 | is.na(extract$notes), "", extract$notes)
type     <- ifelse(dim(extract)[1] == 0, "", extract$vartype)
```

**Variable:** `r variable`  
**Description/Question** `r description`  
**Type:** `r type` 

```{r echo = F}
if (dim(extract)[1] != 0) {


DT::datatable(extract$table[[1]], options = list(pageLength = 50, lengthChange = FALSE,
  bPaginate = FALSE, dom = 't', columnDefs = list(list(className = 'dt-left', targets = "_all"))
), rownames = F) %>% DT::formatStyle(names(extract$table[[1]]),lineHeight='70%') 
}
```
  
**Universe:** `r universe`    
**Notes:** `r notes`  

2002 only
=====================================

Column {data-width=650}
-----------------------------------------------------------------------
### Female, 2002
```{r include= F}
year1 <- "2002"
type1 <- "Female"
extract <- alldata %>% filter(year==year1 & type == type1) 
variable <- ifelse(dim(extract)[1] == 0, "Variable does not exist in this survey/wave", extract$varname)
description <- ifelse(dim(extract)[1] == 0, "", extract$question)
universe <- ifelse(dim(extract)[1] == 0, "", extract$universe)
notes <- ifelse(dim(extract)[1] == 0 | is.na(extract$notes), "", extract$notes)
type     <- ifelse(dim(extract)[1] == 0, "", extract$vartype)
```

**Variable:** `r variable`  
**Description/Question** `r description`  
**Type:** `r type` 

```{r echo = F}
if (dim(extract)[1] != 0) {


DT::datatable(extract$table[[1]], options = list(pageLength = 50, lengthChange = FALSE,
  bPaginate = FALSE, dom = 't', columnDefs = list(list(className = 'dt-left', targets = "_all"))
), rownames = F) %>% DT::formatStyle(names(extract$table[[1]]),lineHeight='70%') 
}
```
  
**Universe:** `r universe`    
**Notes:** `r notes`  

Column {data-width=650}
-----------------------------------------------------------------------

### Male, 2002
```{r include= F}
year1 <- "2002"
type1 <- "Male"
extract <- alldata %>% filter(year==year1& type == type1) 
variable <- ifelse(dim(extract)[1] == 0, "Variable does not exist in this survey/wave", extract$varname)
description <- ifelse(dim(extract)[1] == 0, "", extract$question)
universe <- ifelse(dim(extract)[1] == 0, "", extract$universe)
notes <- ifelse(dim(extract)[1] == 0 | is.na(extract$notes), "", extract$notes)
type     <- ifelse(dim(extract)[1] == 0, "", extract$vartype)
```

**Variable:** `r variable`  
**Description/Question** `r description`  
**Type:** `r type` 

```{r echo = F}
if (dim(extract)[1] != 0) {


DT::datatable(extract$table[[1]], options = list(pageLength = 50, lengthChange = FALSE,
  bPaginate = FALSE, dom = 't', columnDefs = list(list(className = 'dt-left', targets = "_all"))
), rownames = F) %>% DT::formatStyle(names(extract$table[[1]]),lineHeight='70%') 
}
```
  
**Universe:** `r universe`    
**Notes:** `r notes`
 

